\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-30 doc/paper.tex
correcting description of SM fermion mass calculation.
Note: mt is calculated from mt^pole.  The top self-energies miss the
pure QCD corrections, which are added separately.  mb and mtau are
calculated from MS-bar/DR-bar masses, which already contain photon and
QCD contributions.  Therefore in Sigma_{b,tau} these contributions
must be omitted.

    \re\Sigma_{t}^{S,\text{heavy}}(m_t^\text{pole}) \\

@@

    \left[ \re\Sigma_{t}^{L,\text{heavy}}(m_t^\text{pole}) +
      \re\Sigma_{t}^{R,\text{heavy}}(m_t^\text{pole}) + \Delta

@@

where the $\Sigma_{f}^\text{heavy}$ is the self-energy of fermion $f$
without the Standard Model contributions.  The labels $L,R,S$ denote
the left-, right- and non-polarized part of the self-energy.  The
appearing QCD corrections $\Delta m_t^{(1),\text{qcd}}$ and $\Delta
m_t^{(2),\text{qcd}}$ are taken from \cite{Bednyakov:2002sf} and read

@@

      g_2^2}{128 \pi^2} + \frac{13 g_Y^2}{1152 \pi^2}\right) .

@@

The \DRbar mass of the $\tau$ is calculated as

@@

To convert the fermion masses from the \MSbar to the \DRbar scheme the
Yukawa coupling conversion from \cite[Eq.~(19)]{Skands:2003cj} is used
and it is assumed that the VEV is defined in the \DRbar scheme.

>>>>

    \re\Sigma_{t}^{S}(m_t^\text{pole}) \\

@@

    \left[ \re\Sigma_{t}^{L}(m_t^\text{pole}) +
      \re\Sigma_{t}^{R}(m_t^\text{pole}) + \Delta

@@

where the $\Sigma_{t}$ is the top one-loop self-energy without QCD
contributions.  The labels $L,R,S$ denote the left-, right- and
non-polarized part of the self-energy.  The separated QCD corrections
$\Delta m_t^{(1),\text{qcd}}$ and $\Delta m_t^{(2),\text{qcd}}$ are
taken from \cite{Bednyakov:2002sf} and read

@@

      g_2^2}{128 \pi^2} + \frac{13 g_Y^2}{1152 \pi^2}\right) ,

@@

and the \DRbar mass of the $\tau$ is calculated as

@@

In the above equations $\Sigma_{b,\tau}^{\text{heavy}}$ are the
one-loop self-energies of the bottom and $\tau$, where contributions
from the gluon and photon are omitted.  To convert the fermion masses
from the \MSbar to the \DRbar scheme the Yukawa coupling conversion
from \cite{Martin:1993yx} is used and it is assumed that the VEV is
defined in the \DRbar scheme.
